%-------------------------
% Resume in Latex
% Author : Aras Gungore (refactored)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

%---------- PACKAGES ----------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}
\pdfgentounicode=1  % moved here, logically belongs with packages/preamble setup

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

%---------- PAGE STYLE ----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%---------- MARGINS ----------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%---------- SECTION FORMATTING ----------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%---------- SHARED LAYOUT PRIMITIVE ----------
% All subheading commands are built on this two-column tabular row.
% #1 left content  #2 right content
\newcommand{\resumeRow}[2]{%
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    #1 & #2 \\
  \end{tabular*}\vspace{-7pt}%
}

%---------- SUBHEADING VARIANTS ----------
% Single line (bold left, plain right)
\newcommand{\resumeSubheadingSingle}[2]{%
  \resumeRow{\textbf{#1}}{#2}%  % was missing \textbf in original — added for consistency
}

% Two lines (bold+date / italic role+date)
\newcommand{\resumeSubheading}[4]{%
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}%
}

% Three lines (bold+date / subtitle / italic role+date)
\newcommand{\resumeSubheadingTriple}[5]{%
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \small #3   &    \\
    \textit{\small#4} & \textit{\small #5} \\
  \end{tabular*}\vspace{-7pt}%
}

% Five lines (bold+date / subtitle / three italic role+date pairs)
\newcommand{\resumeSubheadingQuad}[9]{%
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \small #3   &    \\
    \textit{\small#4} & \textit{\small #5} \\
    \textit{\small#6} & \textit{\small #7} \\
    \textit{\small#8} & \textit{\small #9} \\
  \end{tabular*}\vspace{-7pt}%
}

% Education heading: institution + degree + two bullet items
% Args: #1 institution  #2 location  #3 degree  #4 dates
%       #5 GPA label    #6 (unused, kept for arity)
%       #7 thesis label #8 (unused, kept for arity)
\newcommand{\resumeEducationHeading}[8]{%
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
  \resumeItemListStart
    \resumeItem{#5}
    \resumeItem{#7}
  \resumeItemListEnd%
}

% Project heading (small font, no bold)
\newcommand{\resumeProjectHeading}[2]{%
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}%
}

%---------- ITEM COMMANDS ----------
\newcommand{\resumeItem}[1]{%
  \item\small{{#1 \vspace{-2pt}}}%
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

%---------- LIST ENVIRONMENTS ----------
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{%
  \begin{itemize}[leftmargin=0.15in, label={}]%
}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%---------- PUBLICATIONS ENVIRONMENT ----------
% Replaces the bare-text + manual \vspace hacks in the Publications section.
% Each entry is a normal \item so spacing is consistent and easy to add/remove entries.
\newenvironment{publist}{%
  \begin{itemize}[leftmargin=0.15in, label={}, itemsep=0.5em, topsep=0pt]%
}{\end{itemize}}

% Convenience macro for a single publication entry
\newcommand{\pubentry}[1]{\item\small{#1}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%---------- HEADING ----------
\begin{center}
  {\Huge \scshape \textbf{Nguyen Vu Binh Duong}} \\ \vspace{3pt}
  \small
  \faMobile \hspace{.5pt} \href{tel:84966997401}{+84 966 997 401}
  $|$
  \faAt \hspace{.5pt} \href{mailto:nguyenvubinhduong@gmail.com}{nguyenvubinhduong@gmail.com}
  $|$
  \faMapMarker \hspace{.5pt} Vietnam
\end{center}

%---------- EDUCATION ----------
\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{\parbox{0.75\textwidth}{University of Engineering and Technology, Vietnam National University (VNU-UET)}}{Hanoi, Vietnam}
{M.Sc. in Software Engineering}{2023 \textbf{--} 2025}
{\textbf{GPA}: 3.87/4.00}{}
{\parbox{0.8\textwidth}{\textbf{Master's Thesis}: AI-based Software System for Early Diagnosis and Detection of Alzheimer's Disease in Vietnamese People}}{}

\resumeEducationHeading
{University of Engineering and Technology, Vietnam National University}{Hanoi, Vietnam}
{B.Sc. in Computer Science}{2019 \textbf{--} 2023}
{\textbf{GPA}: 3.60/4.00}{}
{\parbox{0.8\textwidth}{\textbf{Bachelor's Thesis}: Improving the Performance of Unit Test Case Execution for C/C++ Projects}}{}

\resumeSubHeadingListEnd

%---------- RESEARCH EXPERIENCE ----------
\section{Research Experience}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheadingTriple
{International University, Vietnam National University Ho Chi Minh City}{HCMC, Vietnam}
{Brain Health Lab, School of Biomedical Engineering}
{Researcher}{2024 \textbf{--} Present}
\resumeItemListStart
\resumeItem{Alzheimer's Biomarker Cross-border Development (ABCD) Project, Vietnamese-Swiss Joint Research Programme. Supervisor: Assoc. Prof. Huong Ha}
\begin{itemize}
  \item Developed a modular machine learning framework, comprising predictor and explainer modules, for Alzheimer's disease (AD) classification using structural MRI data from a Vietnamese cohort (N=113).
  \item Identified the Generalized Additive Model as the most interpretable and robust approach (78.8\% accuracy, 87.2\% AUC) for the Vietnamese cohort, balancing performance with clinical explainability.
  \item Conducted a comparative analysis of structural features between the Vietnamese cohort (N=76, from April 30th Hospital) and the ADNI cohort (N=80).
  \item Showed that cross-dataset validation resulted in an approximate 10\% to 25\% drop in prediction accuracy, highlighting the need for population-specific ML models.
\end{itemize}
\resumeItemListEnd

\resumeSubheadingQuad
{University of Engineering and Technology, Vietnam National University}{Hanoi, Vietnam}
{Department of Software Engineering, Faculty of Information Technology}
{Lab Instructor/Research Assistant}{2023 \textbf{--} Present}
{Undergraduate Research Assistant}{2021 \textbf{--} 2023}
{}{}
\vspace{-1.5em}
\resumeItemListStart
\resumeItem{AKAUTAUTO: a proprietary software used for C/C++ unit testing with automated unit test generation. Supervisor: Assoc. Prof. Pham Ngoc Hung}
\begin{itemize}
  \item Directed the research group and facilitated weekly technical reviews with the joint development team at FPT Software.
  \item Provided training and technical consultation to group members.
  \item Researched and implemented an optimized pairwise test case generation and integrated it with the classification tree feature.
  \item Developed a method to stub functions from built-in or external dependencies.
\end{itemize}
\resumeItemListEnd

\resumeSubHeadingListEnd

%---------- PUBLICATIONS ----------
\section{Publications}
\vspace{2pt}
\begin{publist}
  \pubentry{Duy-Thanh Vu, \textbf{Duong Nguyen Vu Binh}, Oliver Y. Chén, Huong Ha \& et al. \textit{Bridging Kernel and Feature Spaces: A New Approach to Accurate and Interpretable Alzheimer's Disease Assessment.} In preparation.}

  \pubentry{\textbf{Duong Nguyen Vu Binh}, Duy-Thanh Vu, Duy-Cat Can, Hai Dac Nguyen, Binh T. Nguyen, Oliver Y. Chén \& Huong Ha. \textit{A Comparison of Machine Learning Methods for Alzheimer's Disease Classification in Vietnamese Patients.} International Symposium on Information and Communication Technology (SOICT 2025). Accepted.}

  \pubentry{Nguyen, M., \textbf{Duong, N. V. B.}, Duc, V. T., Phan, C., Phan, T., \& Ha, H. (2024, July). \textit{Unveiling Heterogeneity in Early Alzheimer's Disease: A Data-Driven Exploration of Mild Cognitive Impairment and Normal Cognition.} In International Conference on the Development of Biomedical Engineering in Vietnam (pp. 408-427). Cham: Springer Nature Switzerland.}

  \pubentry{Nguyen Tung, L., \textbf{Binh Duong, N. V.}, Le, K. N., \& Hung, P. N. (2024). \textit{Automated test data generation and stubbing method for C/C++ embedded projects.} Automated Software Engineering, 31(2), 52.}
\end{publist}

%---------- PRESENTATIONS ----------
\section{Presentations}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeSubheading{Oral Presentation}{}{}{}
\vspace{-20pt}
\resumeItemListStart
\resumeItem{``Unveiling Heterogeneity in Early Alzheimer's Disease: A Data-Driven Exploration of Mild Cognitive Impairment and Normal Cognition.'' at 10th International Conference on the Development of Biomedical Engineering in Vietnam}
\resumeItem{``A Comparison of Machine Learning Methods for Alzheimer's Disease Classification in Vietnamese Patients'' at International Symposium on Information and Communication Technology (SOICT 2025).}
\resumeItemListEnd

\resumeSubheading{Poster Presentation}{}{}{}
\vspace{-20pt}
\resumeItemListStart
\resumeItem{``Machine Learning-Based Analysis of Brain Atrophy Patterns in Alzheimer's Disease: A Comparative Study Between ADNI and Vietnamese Cohorts'' at International Conference on Knowledge and Data Acquisition and Applications \& Asia-Pacific Symposium on Affective Science and Alzheimer's Disease (IC-KDA \& ASAD 2025).}
\resumeItemListEnd

\resumeSubHeadingListEnd

%---------- AWARDS & HONORS ----------
\section{Awards and Honors}
\vspace{2pt}
\resumeSubHeadingListStart
\resumeSubheadingSingle{IC-KDA Asian Society Against Dementia Conference Travel Grant, Korea}{2025}
\resumeSubheadingSingle{Vingroup Innovation Foundation Master's Scholarship, Vietnam}{2024 -- 2025}
\resumeSubheadingSingle{Second prize, The Scientific Research Conference for Undergraduates at VNU-UET, Vietnam}{2023}
\resumeSubHeadingListEnd

%---------- TEACHING ----------
\section{Teaching}
\vspace{2pt}
\resumeSubHeadingListStart
\resumeSubheadingSingle{Advanced Programming (INT2215) $\mid$ Lecturer}{2025 -- Present}
\resumeSubheadingSingle{Object-Oriented Programming (INT2204) $\mid$ Lecturer}{2025 -- Present}
\resumeSubheadingSingle{Object-Oriented Programming (INT2204) $\mid$ Lab Instructor}{2023 -- Present}
\resumeSubheadingSingle{Introduction to Informatics (INT1004 \& INT1376) $\mid$ Lab Instructor}{2023 -- 2025}
\resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
              \textbf{MRI processing:}{ CAT12, CONN} \\ \vspace{3pt}
              \textbf{Programming:}{ Python, JavaScript, C++, LaTeX} \\ \vspace{3pt}
              \textbf{Languages:}{ Vietnamese (native), English (IELTS 7.5 and TOELF IBT 106/120)} \\ \vspace{3pt}
        }}
\resumeSubHeadingListEnd

%---------- REFERENCES ----------
\section{References}
\vspace{2pt}

\textbf{Assoc. Prof. Pham Ngoc Hung}

\vspace{0.25em}
Vice Dean $\mid$ Faculty of Information Technology, University of Engineering and Technology, Vietnam National University

\vspace{0.25em}
Email: hungpn@vnu.edu.vn

\vspace{0.5em}

\textbf{Assoc. Prof. Huong Ha}

\vspace{0.25em}
Chair $\mid$ Department of Tissue Engineering and Regenerative Medicine, School of Biomedical Engineering, International University, Vietnam National University Ho Chi Minh City

\vspace{0.25em}
Email: htthuong@hcmiu.edu.vn

\end{document}